---
title: "SushrutRproject"
author: "Sushrut Vyawahare"
date: "December 30, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# R Project #

# Readind the file #
```{r}
getwd()
setwd("C:/Users/DELL/Documents/Imarticus_data")
diabetes <- read.csv("diabetes_allcols.csv")
names(diabetes)
head(diabetes)
str(diabetes)
summary(diabetes)
diabetes1 <- subset(diabetes,select=-c(encounter_id, patient_nbr, examide,
                                       citoglipton,weight, payer_code, medical_specialty)) 
names(diabetes1)
names(diabetes)
```

#Basic summary of selected data and correlation plot of numeric data
```{r}
library(dplyr)
library(corrplot)
summary(diabetes)
num_diabetes <- select_if(diabetes, is.numeric)
c <- cor(num_diabetes, use= "pairwise.complete.obs")
corrplot(c)
```

#Data cleaning 
```{r}
diabetes2 <- diabetes1[diabetes1$race !="?",]
diabetes2 <- diabetes2[diabetes2$diag_1 !="?",]
diabetes2 <- diabetes2[diabetes2$diag_2 !="?",]
diabetes2 <- diabetes2[diabetes2$diag_3 !="?",]
str(diabetes2)
names(diabetes2)
```

#Binary Representation of readmitted #
```{r}
diabetes2$readmitted <- ifelse(diabetes2$readmitted == "<30",1,0)
table(diabetes2$readmitted)
```

#To make factor level #
```{r}
diabetes3 <-cbind(diabetes2[c(7:13,17)],lapply(diabetes2[c(1:6,14:16,18:43)],
                                               factor))
str(diabetes3)
head(diabetes3)
```

#Table to get frquency of different levels of readmission#
```{r}
table(diabetes3$readmitted)

prop.table(table(diabetes3$readmitted))

table(diabetes3$readmitted)  
```

#check region wise #
```{r}
racewise <- table(diabetes3$readmitted,diabetes3$race)
racewise
```

#Check Gender wise#
```{r}
genderwise <- table(diabetes3$readmitted,diabetes3$gender)
genderwise
```

#Check Age wise#
```{r}
agewise <- table(diabetes3$readmitted,diabetes3$age)
agewise
```

#ploting graph  readmitted #
```{r}
library(ggplot2)
plot(table(diabetes$readmitted),xlab = " Readmission ", main = " Frequency of Readmission")

plot(table(diabetes3$readmitted),xlab = " Readmission ", main = " Frequency of Readmission")
```

#Dividing test and train#
```{r}
library(caret)
library(ggplot2)
library(lattice)
library(kernlab)

inTrain <- createDataPartition(diabetes3$readmitted,p = .2,list = F)
Training <- diabetes3[inTrain,]
Testing <- diabetes3[-inTrain,]

dim(Training)
dim(Testing)
```

#glm method#
```{r}
modFit <- train(readmitted ~ time_in_hospital + num_lab_procedures + num_procedures
                + num_medications+ number_outpatient + number_emergency + 
                  number_inpatient + race + age + admission_type_id + 
                  discharge_disposition_id + admission_source_id  + max_glu_serum + 
                  A1Cresult + metformin + insulin,data = Training,method = "glm")
modFit$finalModel

prediction <- predict(modFit,newdata = Testing)
table(prediction)
confusionMatrix(prediction,Testing$readmitted)
#  Accuracy : 0.8866 #
```

#Rpart# Recursive Partitioning And Regression Trees
```{r}
library(rpart)
modFit1 <- train(readmitted ~ time_in_hospital + num_lab_procedures + num_procedures
                 + num_medications+ number_outpatient + number_emergency + 
                   number_inpatient + race + age + admission_type_id + 
                   discharge_disposition_id + admission_source_id  + max_glu_serum + 
                   A1Cresult + metformin + insulin,data = Training,method = "rpart")
modFit1$finalModel

prediction1 <- predict(modFit1,newdata = Testing)
confusionMatrix(prediction1,Testing$readmitted)
#Accuracy : 0.8872 #
```

#Random Forest #

library(randomForest)
modFit_rf <- train(readmitted ~ time_in_hospital + num_lab_procedures + num_procedures
                  + num_medications+ number_outpatient + number_emergency + 
                    number_inpatient + race + age + admission_type_id + 
                    discharge_disposition_id + admission_source_id  + max_glu_serum + 
                    A1Cresult + metformin + insulin,data = Training,method = 
                    "glm", minsplit = 1, minbucket = 1, cp = 0.001)
print(modFit_rf$finalModel)
plot(modFit_rf$finalModel,uniform = T,main = "Classification Tree")

# SVM Model #
library(e1071)
svmmodel <- svm(readmitted ~ time_in_hospital + num_lab_procedures + num_procedures
                + num_medications+ number_outpatient + number_emergency + 
                  number_inpatient + race + age + admission_type_id + 
                  discharge_disposition_id + admission_source_id  + max_glu_serum + 
                  A1Cresult + metformin + insulin,data = Training,kernel = "linear",
                type = "C-classification", cross = 10, cost = 0.01, gamma = 1000)
summary(svmmodel)
prediction2 <- predict(summodel,newdata = Testing)
confusionMatrix(prediction2,Testing$readmitted)

#Performance 
result <-as.data.frame(table(prdiction2,Testing$readmitted)) 
result 
CorrectlyPredicted <- result[1,3] + result[4,3] 
accuracy <- CorrectlyPredicted / nrow(test) 
accuracy 
senstivity_result <- result[4,3] / (result[2,3] + result[4,3]) 
senstivity_result  
specificity_result <- result[1,3] / (result[3,3] + result[1,3]) 
specificity_result 
